Proposed Solution

### 2017-01-25 CAV17/secs/postanal.tex

We will also denote $E_{V_1, V_2} \subset E$ as the \textit{slice set} of $E$ over $V_1, V_2$:

@@

We can think of $E_{V_1, V_2}$ as being the subset of edges in $E$ 
such that each source set $V_s$ shares a vertex with $V_1$
and each target set $V_t$ shares a vertex with $V_2$.
We denote a naked vertex $v$ in our subscripts as notational 
convenience for the singleton set containing that vertex $v$.

>>>>

We will also denote $E_{V_1, V_2} \subset E$ as the \textit{slice set} 
of $E$ over $V_1, V_2$.
We can think of $E_{V_1, V_2}$ as being the subset of edges in $E$ 
such that each source set $V_s$ shares a vertex with $V_1$
and each target set $V_t$ shares a vertex with $V_2$.
Formally:

@@

We denote a standalone vertex $v$ in our subscripts as notational 
convenience for the singleton set containing that vertex $v$.
